\begin{abstract}
This engineering thesis raises subject of Points Of Interest (POI) categorization. The topic of thesis is very broad and complex and may relate to many smaller subtopics.

During the process of thesis creation there was done research about possible methods which can be useful in text categorization. As a practical part there was designed and implemented a simple information system enabling POI categorization. The form of information system is java library which can be used by any programmer in java desktop or mobile application (android). Usage of library is very simple and intuitive the only requirement is to import .jar file (which is result of this thesis) to java project in integrated development environment (IDE).

Part of resultant java library is \textit{loadstone} database which was created from files available on website. \cite{29} Downloaded text files were converted to SQLite database for data access convenience using \textit{bash} shell script which was created specially for this purpose. Java library delivers easy to use set of methods for POI categorization as well interface to access \textit{SQLite} database in object relational mapping way. Such functionality exempt programmer from \textit{SQL} query knowledge and enables using database using only java methods.

Compelling part of thesis are presented results of POI categorization. Results pays special attention to results correctness and performance. Another important part is description architecture including UML diagram and more human-readable picture depicting overall library architecture.

Application was developed using \textit{maven} tool which manages third party dependencies and project building. As a version control system application called \textit{Git} was used and source code repository is available on website. \cite{30}     
\end{abstract}